### 2023-05-24 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

% \begin{algorithm}
%     \caption{STEP sequence in controller thread}\label{alg:stepping_algorithm}
%     \begin{algorithmic}
%     \Procedure{STEP}{$voltage\_start,voltage\_stop$} 
%         \State $voltage \gets voltage\_start$
%         \While{$voltage \leq voltage\_stop$} \Comment{scanning voltage range}
%             \State \Call{send\_voltage\_command}{voltage}
%             \State \Call{sleep}{step \_time}
%             \State $voltage \gets voltage + step\_size$
%         \EndWhile
%     \EndProcedure

%     \end{algorithmic}
% \end{algorithm}

@@

\begin{figure}[H]
    \center
    \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
    \caption{Domains of existence (stability) of Taylor Cone Jets. \cite{gananCalvo} .}
    \label{fig:ganan_calvo_fig}
\end{figure}

    To reach certain map it is necessary to traverse flow rate (X axis) and voltage (Y axis) values acquiring samples.
    In Figure \ref{fig:map2Data_fig} it can be seen how the mapping procedure works. The liquid used is pure ethanol. 
    Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.

>>>>

@@

\begin{figure}[H]
    \center
    \includegraphics[width=15cm]{Figuras/ganan_calvo_map.png}
    \caption{Domains of existence (stability) of Taylor Cone Jets. \cite{gananCalvo} .}
    \label{fig:ganan_calvo_fig}
\end{figure}

    \vspace{2cm}
    To reach certain map it is necessary to traverse flow rate (X axis) and voltage (Y axis) values acquiring samples.
    In Figure \ref{fig:map2Data_fig} it can be seen how the mapping procedure works. The liquid used is pure ethanol. 
    Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.
